---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  #out.width = "100%",
  fig.path = "man/figures/README-"
)
```

# promedreadr

<!-- badges: start -->
[![Build Status](https://travis-ci.com/epiben/promedreadr.svg?token=jPFag7F7DJzmhXYLiSqy&branch=main)](https://travis-ci.com/epiben/promedreadr)
![Version](https://img.shields.io/badge/version-0.1.0-informational.svg)
<!-- badges: end -->

The goal of `promedreadr` is to provide a simple tool for collecting information from https://pro.medicin.dk, a key reference on medicines marketed in Denmark. 

Note that the package is not yet "production ready", especially it doesn't yet honour robots.txt (improvement is underway and will be up shortly.)

## Just because you can doesn't mean you should
Please use this package thoughtfully as web-scraping can lead to e.g. copyright infringement. If in doubt, please contact the team behind [medicin.dk](https://www.medicin.dk).

## Features

- Simple interface for querying based on ATC codes
- Marshals information from all products containing drugs with the queried ATC code(s)
- Reconciles side effects reported across products and rolls them up to the ATC code(s)
- Can produce handy, single-line lists of side effects, by frequencies

## Example

```{r example}
library(promedreadr)

atc_codes <- c(Quetiapin = "N05AH04",
			   Lithium = "N05AN01")

product_urls <- extract_product_urls(atc_codes)
all_ade_tables <- fetch_ade_tables(product_urls)
combined_ade_tables <- reconcile_ade_tables(all_ade_tables)

combined_ade_tables
```

## Installation

`promedreadr` isn't yet on CRAN, but you can install it easily directly from [GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("devtools") # if not already installed
remotes::install_github("epiben/promedreadr")
```

## Contributing

We use the [GitHub issue tracker](https://www.github.com/epiben/promedreadr/issues) for all bugs/issues/enhancements

## License

`promedreadr` is licensed under the MIT licence.

## Development and status

`promedreadr` is developed in RStudio and maturing under active development.

## Acknowledgements

The package maintainer received funding from Innovation Fund Denmark (5153-00002B) and the Novo Nordisk Foundation (NNF14CC0001).
